Appendix 1.F: Analysing global trends in within-country inequality

### 2023-02-01 PhD_pages/data_appendices/1_F_within_country_trends.qmd
Tidying names and layout

```{shinylive-python}
#| standalone: true
#| viewerHeight: 420

@@

```{shinylive-python}
#| standalone: true
#| viewerHeight: 420

#  ---------------------------------
#  ---------- Data prep functions -------------
#  ----------------------------------

#  ---------------------------------
#  ---------- Specifications -------------
#  ----------------------------------

source_count_requirement = 2

app_ui = ui.page_fluid(
    {"class": "p-4"},
    ui.row(
        ui.column(
            4,
            panel_box(
                ui.input_slider("reference_vals", "Reference years", 1975, 2020, value=[1990,2018]),
                ui.input_numeric(
                            "max_dist_from_refs",
                            "=/- (years)",
                            4,
                        ),
                ui.input_numeric(
                            "min_dist_between",
                            "Min distance between observations (years)",
                            23,
                        ),
                ui.input_action_button(
                    "download", "Download data and image", class_="btn-primary w-100"
                ),
            ),
            ui.navset_tab_card(
                ui.nav(
                    "Compare sources",
                    ui.input_select(
                "metric",
                "Metric",
                {
                    "Gini": "Gini",
                    "Top_10_share": "Top 10p.c. share",
                },
            ),
            ),
                ui.nav(
                  "Compare metrics"),
            ),
        ),
        ui.column(
            8,
            ui.output_plot("example_plot")
            ),
    ),
)

      def prep_wid_pip_data(reference_vals, max_dist_from_refs, min_dist_between, reference_col, group_by_col, value_col):

        pip_matches = pip_welfare_routine(
          df = df_pip,
          reference_vals = reference_vals,
          max_dist_from_refs = max_dist_from_refs,
          min_dist_between = min_dist_between,
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = value_col
        )

        wid_matches = merge_two_ref_matches(
          df = df_wid,
          reference_vals = reference_vals,
          max_dist_from_refs = max_dist_from_refs,
          min_dist_between = min_dist_between,
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = value_col
        )

        ref_pairs = pd.concat([pip_matches, wid_matches,], keys=['pip', 'wid'])

        # Tidy up indexes
        ref_pairs = ref_pairs.reset_index()

        ref_pairs = ref_pairs.drop('level_1', axis=1)

        ref_pairs = ref_pairs\
          .rename(columns={"level_0": "source"})

        return ref_pairs

      def prep_plot_and_tables(
        reference_vals, 
        max_dist_from_refs,
        min_dist_between,
        reference_col,
        group_by_col,
        value_col,
        tolerance,
        outlier_cut_off_upper,
        source_count_requirement):

        plot_data = prep_wid_pip_data(
          reference_vals = reference_vals, 
          max_dist_from_refs = max_dist_from_refs,
          min_dist_between = min_dist_between,
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = value_col,
        )

        # Store the names of the columns to be used onthe X and Y axis
        x_axis = f'{value_col}{reference_vals[0]}'
        y_axis = f'{value_col}{reference_vals[1]}'

        # Add a count by country – showing whether data is available from both sources or not
        plot_data['source_count'] = plot_data.groupby(group_by_col)['source'].transform('count')

        # Apply source requirement (whether to include only observations with data from both sources)
        plot_data = plot_data.loc[plot_data['source_count'] >= source_count_requirement]

        plot = (ggplot(plot_data
        , aes(x_axis, y_axis, alpha=0.5))
        + geom_point(aes(color=region_col, size='avg_pop', alpha = 0.6))
        + facet_wrap('~ source')
        + geom_polygon(aes(x='x', y='y', alpha = 0.2), data=shaded_coord)
        + theme_light()
        + theme(legend_position='none')
        )

        group_yes_vars = ['source', region_col]
        group_no_vars = ['source']

          agg_level['global_pop_weights'] = agg_level.groupby('source')['avg_pop'].transform(lambda x: x/x.sum())

      plot_and_tables = prep_plot_and_tables(
          reference_vals = list(input.reference_vals()), 
          max_dist_from_refs = input.max_dist_from_refs(),
          min_dist_between = input.min_dist_between(),
          reference_col = reference_col,
          group_by_col = group_by_col,
          value_col = input.metric(),
          tolerance = tolerance,
          outlier_cut_off_upper = outlier_cut_off_upper,
          source_count_requirement = source_count_requirement
          )

>>>>

```{shinylive-python}
#| standalone: true
#| viewerHeight: 1000

@@
